---
title: Antibody Property Report


output: 
  html_document:
   theme: united

params:
  a: "NULL"
  b: "NULL"
  c: "NULL"
  d: "NULL"
  e: "NULL"
  f: "NULL"
  g: "NULL"
  h: "NULL"
  i: "NULL"
  j: "NULL"
  k: "NULL"
  l: "NULL"
  m: "NULL"
  o: "NULL"
  p: "NULL"
  q: "NULL"
  A: "NULL"
  B: "NULL"
  D: "NULL"
  E: "NULL"
  H: "NULL"
  I: "NULL"
  M: "NULL"
---



<style type="text/css">


h1.title {
  font-size: 38px;
  color: Black;
}
h1 { /* Header 1 */
  font-size: 28px;
  color: DarkBlue;
}
h2 { /* Header 2 */
  font-size: 28px;
  color: DarkBlue;
}
h3 { /* Header 3 */
  font-size: 22px;
  text-align: justify;
}
h5 { /* Header 5 */
  font-family: "Courier"; font-size: 14px;
}

</style>

##### `r params$o`  


<div style="margin-bottom:100px;">
```{r loading packages and functions, echo=FALSE, results='hide', message=FALSE, warning=FALSE}
library(dplyr)
library(kableExtra)

```


</div>
### Therapeutic antibody ``r params$m`` is  `r  params$p`, it contains, in total, `r (params$j+params$k)*2` amino acids, with **extinction coefficient (EC)** of  *`r params$l` /(m cm)*, based on `r params$E` tryptophan, `r params$H` tyrosine, `r params$I` cystine`r params$M`.[^1] ``r params$m`` has `r (params$q)*2` glycan sites.
<div style="margin-bottom:40px;">
</div>
## **Sequence Display** 
### **Heavy chain** sequence (`r params$j` amino acids):  
##### `r params$f`

### **Light chain** sequence (`r params$k` amino acids):    
##### `r params$g`  



## **amino acids composition**  Table

```{r HC AA, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$h, caption = "Heavy Chain Residue Composition", format = "html", align="c") %>% kable_styling(bootstrap_options = c("striped","condensed","responsive","hover"))  %>%
  column_spec(1, bold = T, color = "red") %>%
  row_spec(0, bold = T)
```



```{r LC AA, echo=FALSE, results= 'asis', message=FALSE, warning=FALSE}
knitr::kable(params$i, caption = "Light Chain Residue Composition", format = "html", align="c") %>% kable_styling(bootstrap_options =  c("striped","condensed","responsive","hover"))  %>%
  column_spec(1, bold = T, color = "red") %>%
  row_spec(0, bold = T)
```


<div style="margin-bottom:50px;">
</div>

## **Theoretical Masses** Table [^2]  
### *Non-reduced Calculations (theoretical)*    

```{r theo nR, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$A, caption = "Non-reduced Masses and Formulas",format = "html",row.names = FALSE, align = "c", col.names = c("HC-pE","LC-pE","CtermK removal","Glycan","DSB","C","H","N","O","S","Mass")) %>% kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=5,"Compositions"=5," "=1)) %>%
column_spec(6, border_left = T) %>%
  column_spec(11, border_left = T, bold = T)
 
```
<div style="margin-bottom:50px;">
</div>
### *Reduced Calculations (theoretical)*
### **Heavy Chain**  
```{r theo HC fully Reduced, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$B, caption = "Fully-reduced Heavy Chain", format = "html", row.names = FALSE,  align = "c", col.names = c("HC-pE", "CtermK removal", "Glycan", "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>% 
  column_spec(4, border_left = T) %>%
  column_spec(9, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=3,"Compositions"=5," "=1))
  
```

<div style="margin-bottom:50px;">
</div>
### **Light Chain**  

```{r theo LC fully Reduced, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$D, caption = "Fully-reduced Light Chain", format = "html",  row.names = FALSE,  align = "c", col.names = c("LC-pE" , "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>% 
  column_spec(2, border_left = T) %>%
  column_spec(7, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=1,"Compositions"=5," "=1))
  
```

<div style="margin-bottom:70px;">
</div>
## **Expected Masses** Table [^3] 
### *Non-reduced Calculations (expected)*    

```{r nR, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$a, caption = "Non-reduced Masses and Formulas",format = "html",row.names = FALSE, align = "c", col.names = c("HC-pE","LC-pE","CtermK removal","Glycan","DSB","C","H","N","O","S","Mass")) %>% kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=5,"Compositions"=5," "=1)) %>%
column_spec(6, border_left = T) %>%
  column_spec(11, border_left = T, bold = T)
 
```

<div style="margin-bottom:50px;">
</div>
### *Reduced Calculations (expected)*
### **Heavy Chain** 

```{r HC fully Reduced, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$b, caption = "Fully-reduced Heavy Chain", format = "html", row.names = FALSE,  align = "c", col.names = c("HC-pE", "CtermK removal", "Glycan", "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>% 
  column_spec(4, border_left = T) %>%
  column_spec(9, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=3,"Compositions"=5," "=1))
  
```



```{r HC withDSB, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$c, caption = "Heavy Chain with unreduced intra-chain disulfide bonds", format = "html", row.names = FALSE, align = "c", col.names = c("HC-pE", "CtermK removal", "Glycan", "#.UnReduced DSB", "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>% 
  column_spec(5, border_left = T) %>%
  column_spec(10, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=4,"Compositions"=5," "=1))
  
```

<div style="margin-bottom:50px;">
</div>
### **Light Chain**  

```{r LC fully Reduced, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$d, caption = "Fully-reduced Light Chain", format = "html",  row.names = FALSE,  align = "c", col.names = c("LC-pE" , "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options = c("striped","condensed","responsive","hover")) %>% 
  column_spec(2, border_left = T) %>%
  column_spec(7, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
  add_header_above(c("Modifications"=1,"Compositions"=5," "=1))
  
```


```{r LC withDSB, echo=FALSE, results='asis', message=FALSE, warning=FALSE}
knitr::kable(params$e, caption = "Light Chain with unreduced intra-chain disulfide bonds", format = "html",row.names = FALSE, align = "c", col.names = c("LC-pE" , "#.Unreduced DSB", "C","H","N","O","S","Mass")) %>%  kable_styling(bootstrap_options  = c("striped","condensed","responsive","hover")) %>% 
  column_spec(3, border_left = T) %>%
  column_spec(8, border_left = T, bold = T) %>%
  row_spec(0, bold = T) %>%
   add_header_above(c("Modifications"=2,"Compositions"=5," "=1))
 
```



##### software version: v1.0  

[^1]: Theoretical extinction coefficient was calculated using the Edelhoch method but with the extinction coefficients for Trp and Tyr determined by Pace et al. Refer to (i) Edelhoch, H. (1967) Spectroscopic determination of tryptophan and tyrosine in proteins. Biochemistry 6, 1948-1954. (ii) Pace, C.N., Vajdos, F., Fee, L., Grimsley, G., and Gray, T. (1995) How to measure and predict the molar absorption coefficient of a protein. Protein Sci. 11, 2411-2423.
[^2]: Masses and formulas in *Theoretical Masses* refer to the state of antibody with no terminal modifications, no glycosylations (aglycosylated Asn), the C-term Lys residue and disulfide bonds are retained in this state. Reference averaged atomic masses used in theoretical mass calculations are: "C"=12.0107, "H"=1.00794,"N"=14.0067,"O"=15.9994, "S"=32.0650.
[^3]: Masses and formulas in *Expected Masses* refer to the various states of antibody with considerations of PTMs heterogeneity. Same set of averaged atomic masses are used.
